Environmental stress affects niche breadth in plant-pollinator communities

### 2019-11-16 paper/manuscript.Rmd
Improve results

After performing our sensitivity analysis, we found that we need roughly `r readd(min_occurrences_factor)` independent occurrences for each community for which we calculated a suitability value in order to obtain a mean absolute error below `r config$min_suitability_error` (Fig. \@ref(fig:fig-sensitivity-analysis)). 
We therefore removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
When inspecting the suitability values of the analysed species we found that some communitues have larger overal suitability values. 
However, most communities included species for which habitat suitability was low and species for which it was high (Fig. \@ref(fig:fig-median-suitability)).

@@

We found that our models performed relativelly well.
The bayesian R-squared for our baseline model was `r round(bayesian_r2_baseline[1], digits = 2)`, which indicates our models were able to capture a large proporton of the variability on the data. 
Overall we found only weak evidence of a relationship between the environmental niche size and the normalised degree (Figure \@ref(fig:fig-conditional-effects)a). 
This relationship was stronger for plants than for animals.
Similarly environmental suitability does not show a consistent pattern accross species. 
Indeed, when looking at the population level effects, suitability virtually no relationship with normalised degree, neither for plants or pollinators (Figure \@ref(fig:fig-conditional-effects)b). 
However, suitability is still an important predictor as the WAIC difference between our baseline model and that that did not include suitability was `r round(waic_diff_suitability)` ± `r round(waic_se_diff_suitability)`. 
Both among plants and pollinators for some species there is a strong negative relationship between suitability and normalised degree and some others with a strong positive relationship (Figure \@ref(fig:fig-random-effects)a). 
As expected, we found a positive relationship between a species generalism and normalised degree \@ref(fig:fig-conditional-effects)c). 
However our model comparisons based on WAIC shows that including generalism in the model adds relatively little information once we have accounted for the other variables in the model.
Finally, we found a strong and positive relationship between the number of possible interactions and the number of realised interactions in the community.

@@

```{r tab-model-comparison-table}
model_ranking$waic %>%
  purrr::map(~.$estimates["waic", ]) %>%
  purrr::map_df(~tibble::tibble(estimate = .[1], se = .[2]), .id = "formula") %>%
  dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 
                formula = kableExtra::cell_spec(formula, format = "latex", 
                                                bold =nchar(formula) == max(nchar(formula)))) %>% 
   knitr::kable("latex", 
               booktabs = TRUE, 
               digits = c(0,0,0), 
               format.args = list(big.mark = ","), 
               col.names = c("predictors", "WAIC", "SE"),
               escape = FALSE,
               linesep = "",
               caption = "Comparison in out of sample predictive power of the baseline model (bold) and their alternatives. We rank models by their expected log predictive density based on their leave-one-out cross-validation information criterion (LOO). The standard error of the LOO difference provides rough guidance to the uncertainty of the model ranking. We also show the Wanatabe-Akaike information criterion (WAIC) of each model for comparison.") %>%
  kableExtra::kable_styling(font_size = 8) #%>%
  # kableExtra::add_header_above(c(" " = 1, "LOO" = 3, " " = 1))
# 
# waic_scores <- as.data.frame(model_ranking$waic) %>%
#   tibble::rownames_to_column(var = "formula") %>%
#   dplyr::select(formula, waic)
# 
# loo_scores <- as.data.frame(model_ranking$loo) %>%
#   tibble::rownames_to_column(var = "formula") %>%
#   dplyr::select(formula, elpd_diff, se_diff,  looic) 
# 
# loo_scores %>%
#   dplyr::inner_join(waic_scores, by = "formula") %>%
#   dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 
#                 formula = kableExtra::cell_spec(formula, format = "latex", 
#                                                 bold =nchar(formula) == max(nchar(formula)))) %>%
#   knitr::kable("latex", 
#                booktabs = TRUE, 
#                digits = c(0,0,1,0,0), 
#                format.args = list(big.mark = ","), 
#                col.names = c("predictors", "$\\Delta$", "$SE_{\\Delta}$", "IC", "WAIC"),
#                escape = FALSE,
#                linesep = "",
#                caption = "Comparison in out of sample predictive power of the baseline model (bold) and their alternatives. We rank models by their expected log predictive density based on their leave-one-out cross-validation information criterion (LOO). The standard error of the LOO difference provides rough guidance to the uncertainty of the model ranking. We also show the Wanatabe-Akaike information criterion (WAIC) of each model for comparison.") %>%
#   kableExtra::kable_styling(font_size = 8) %>%
#   kableExtra::add_header_above(c(" " = 1, "LOO" = 3, " " = 1))
```

The group level variation among communities was larger than that among species.
The standard deviation (in the parameters scale) of the community intercepts was `r round(sd_loc_id$Estimate, 2)` [`r round(sd_loc_id$Q2.5, 2)`, `r round(sd_loc_id$Q97.5, 2)`] while the standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' suitability slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] (95% credible intervals shown within square brakets). 
Interestingly, the slope the relationship between suitability and normalised degree was negatively correlated with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b). 
The mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`].

@@

>>>>

After performing our sensitivity analysis, we found that we need roughly `r readd(min_occurrences_factor)` independent occurrences for each community for which we calculated a suitability value in order to obtain a mean absolute error below `r config$min_suitability_error` (Fig. \@ref(fig:fig-sensitivity-analysis)). 
We therefore removed from further analyses `r n_spp_not_enough_occ` species for which we did not have enough occurrences to obtain robust estimates.
When inspecting the suitability values of the analysed species we found that most communities included species for which habitat suitability was low and species for which it was high (Fig. \@ref(fig:fig-median-suitability)).

@@

Our models performed relativelly well.
The bayesian R-squared for our baseline model was `r round(bayesian_r2_baseline[1], digits = 2)`, which indicates our models were able to capture a large proporton of the variability on the data. 
Overall we found that environmental suitability does not show a consistent pattern accross species. 
Indeed, when looking at the population level effects, suitability has virtually no relationship with normalised degree, neither for plants or pollinators (Figure \@ref(fig:fig-conditional-effects)b). 
However, suitability is an important predictor as the WAIC difference between our baseline model and that that did not include suitability was `r round(waic_diff_suitability)` ± `r round(waic_se_diff_suitability)` (Table \@ref(tab:tab-model-comparison)).
This apparent discrepancy can be explained by the variability of the suitability-degree relationship across species.

@@

```{r tab-model-comparison}
model_ranking$waic %>%
  purrr::map(~.$estimates["waic", ]) %>%
  purrr::map_df(~tibble::tibble(estimate = .[1], se = .[2]), .id = "formula") %>%
  dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 
                formula = kableExtra::cell_spec(formula, format = "latex", 
                                                bold =nchar(formula) == max(nchar(formula)))) %>% 
   knitr::kable("latex", 
               booktabs = TRUE, 
               digits = c(0,0,0), 
               format.args = list(big.mark = ","), 
               col.names = c("predictors", "WAIC", "SE"),
               escape = FALSE,
               linesep = "",
               caption = "Comparison in out of sample predictive power of the baseline model (bold) and their alternatives. We rank models by their expected log predictive density based on their leave-one-out cross-validation information criterion (LOO). The standard error of the LOO difference provides rough guidance to the uncertainty of the model ranking. We also show the Wanatabe-Akaike information criterion (WAIC) of each model for comparison.") %>%
  kableExtra::kable_styling(font_size = 8) #%>%
  # kableExtra::add_header_above(c(" " = 1, "LOO" = 3, " " = 1))
# 
# waic_scores <- as.data.frame(model_ranking$waic) %>%
#   tibble::rownames_to_column(var = "formula") %>%
#   dplyr::select(formula, waic)
# 
# loo_scores <- as.data.frame(model_ranking$loo) %>%
#   tibble::rownames_to_column(var = "formula") %>%
#   dplyr::select(formula, elpd_diff, se_diff,  looic) 
# 
# loo_scores %>%
#   dplyr::inner_join(waic_scores, by = "formula") %>%
#   dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 
#                 formula = kableExtra::cell_spec(formula, format = "latex", 
#                                                 bold =nchar(formula) == max(nchar(formula)))) %>%
#   knitr::kable("latex", 
#                booktabs = TRUE, 
#                digits = c(0,0,1,0,0), 
#                format.args = list(big.mark = ","), 
#                col.names = c("predictors", "$\\Delta$", "$SE_{\\Delta}$", "IC", "WAIC"),
#                escape = FALSE,
#                linesep = "",
#                caption = "Comparison in out of sample predictive power of the baseline model (bold) and their alternatives. We rank models by their expected log predictive density based on their leave-one-out cross-validation information criterion (LOO). The standard error of the LOO difference provides rough guidance to the uncertainty of the model ranking. We also show the Wanatabe-Akaike information criterion (WAIC) of each model for comparison.") %>%
#   kableExtra::kable_styling(font_size = 8) %>%
#   kableExtra::add_header_above(c(" " = 1, "LOO" = 3, " " = 1))
```

While for some species there is a strong negative relationship between suitability and normalised degree, for some others with a strong positive relationship (Figure \@ref(fig:fig-random-effects)a). 
Interestingly, the slope this relationship was negatively correlated with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b). 
The mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`].
In other words, the slope of the suitability-degree relationship was more likelt to be positive for species with a smaller number of partners in lower-suitability and negative for species with a larger number of partners in lower-suitability conditions.

@@

As expected, we found a strong and positive relationship between the number of possible interactions and the number of realised interactions in the community. 
There was a large difference on WAIC between the model that included this predictor and that that excluded it. 
This result indicates that the availability of potential partners accounts for a large proportion of the variabiity on species degree.  
Importantly, our findings about the suitability-degree relationship were qualitatively unchanged whether this variable was included or not.

The group level variation among communities was larger than that among species which further indicates the importance of the local context when determining species degree.
Specifically, the standard deviation (in the parameters scale) of the community intercepts was `r round(sd_loc_id$Estimate, 2)` [`r round(sd_loc_id$Q2.5, 2)`, `r round(sd_loc_id$Q97.5, 2)`] while the standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' suitability slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] (95% credible intervals shown within square brakets).
